What Makes New Coders Spend More Money

### 2021-04-26 outputs/paper/paper.Rmd
Edit text in paper.Rmd

>>>>

## Software Used {-}
This paper is written in Rmarkdown [@citeRmarkdown] and `bookdown` [@citeBookdown], and printed by the `knitr` package [@citeKnitr]. The `here` package was used to set the path to the project folder [@citeHere]. And, the `kableExtra` [@citeKable] and `stargazer` [@citeStargazer] packages were used to crate tables.
